### 2024-01-28 README.Rmd
updates readme a bit

Prerequisites:

  - docker
  - nvidia-container-toolkit

@@

## Reports

The **reports** directory currently contains the `GnC_report` folder wich is structured as such:

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder: supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

### Licenses

@@

<!-- **Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

@@

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse -->

@@

<!-- This repository contains the data and code for our paper:

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> -->

>>>>

*Dependencies:*

-   *docker*
-   *nvidia-container-toolkit*

## Report(s) and website

The **reports** directory currently contains the [:file\_folder: paper](/analysis/paper) directory with the Quarto source document for the GnC report. Includes code to reproduce the figures and tables generated by the analysis.

Website is under construction.

@@

````{=html}
<!--
### Licenses

@@

**Text and figures :**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

@@

**Data :** [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

@@

This repository contains the data and code for our paper:

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> 
-->
````
